Outstanding Title

### 2017-03-20 writing/EpiDraft.Rmd
mystery leftovers

---
title: "Outstanding Title"
author: "Sarah Koehler"
date: "February 21, 2017"
output:
  pdf_document: default
  html_document: default
---

>>>>

---
title: "Outstanding Title"
author: "Sarah Koehler"
date: "February 21, 2017"
bibliography: mybibfile.bib
output:
  pdf_document: default
  html_document: default
---
